\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2018-08-30 paper/manuscript.tex
improved captions and re-ordered figures 2-5

\begin{figure}[htp]
	\centering
	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
	\label{boilerplate_before_after1}
	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterNwords.pdf}
\end{figure}
\begin{figure}[htp]
	\centering
	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
	\label{boilerplate_before_after2}
	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterFreq.pdf}
\end{figure}
\begin{figure}[htp]
	\centering
	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
	\label{boilerplate_before_after3}
	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterMedianDocMidDist.pdf}
\end{figure}
\begin{figure}[htp]
	\centering
	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
	\label{boilerplate_before_after4}
	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterNchars.pdf}
\end{figure}

>>>>

\begin{figure}[htp]
	\centering
	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK. After the boilerplate content is removed, extremely short lines are less common.}
	\label{boilerplate_before_after1}
	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterNwords.pdf}
\end{figure}
\begin{figure}[htp]
	\centering
	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK. After the boilerplate content is removed, extremely short lines are less common.}
	\label{boilerplate_before_after2}
	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterNchars.pdf}
\end{figure}
\begin{figure}[htp]
	\centering
	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK. After the boilerplate content is removed, lines that are duplicated hundreds or thousands of times are less common.}
	\label{boilerplate_before_after3}
	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterFreq.pdf}
\end{figure}
\begin{figure}[htp]
	\centering
	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK. After the boilerplate content is removed, lines at the beginning and end of documents are less common.}
	\label{boilerplate_before_after4}
	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterMedianDocMidDist.pdf}
\end{figure}
